What We Eval in the Shadows

### 2021-08-12 paper/main.tex
Update 6.control

\paragraph{Controlled Evaluation}
Developer often want to control when and if expressions are evaluated. For
example, a package that provides users with the ability to make assertions and,
if they fail, produce legible error messages. The example here accepts a vararg
with a list of expressions whose code is extracted using
\k{eval(substitute(alist(...)))}. The expression are evaluated sequentially
in the caller's environment. If an expression is false, an error message is
generated.

>>>>

\paragraph{Controlled Evaluation}
Developer often want to control when and if expressions are evaluated. For
example, a package that provides users with the ability to make assertions and,
if they fail, produce legible error messages. The example here accepts a vararg
with a list of expressions. It extracts the associated code in the same way as
the extracting varags example and evaluates each of the expression sequentially
in the caller's environment. If an expression does not hold, an error is
generated.
